---
title: "Individual Assignment"
output: html_document
---
```{r}
#tinytex::install_tinytex()
```
```{r}

```

```{r}
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(ggpubr)

```




3. Price prediction

3.1. Simple linear regression
```{r}

#install.packages("future")
library(future)
plan(multiprocess, workers = 4)

require(caret)
require(ggfortify)

## Eliminate multicollinarity effect : Keeping Region and Country will lead to the multicollinariy effect

likehome.final <- likehome.final %>%
  select(!c(Region,Country))

train.control <- trainControl(method = "repeatedcv",
                              repeats = 10,
                              number = 10,
                              verboseIter = F)


#Simple linear regression

set.seed(2)

simple.linear.regression <- train(log(Price) ~. -ID -Zipcode -Review.missing -Bathrooms.missing -Bedrooms.missing -Zipcode.missing -Room_type.missing -City.missing,
                                  data = likehome.final,
                                  method = "lm",
                                  metric = "Rsquared",
                                  trControl = train.control)

autoplot(simple.linear.regression$finalModel, which = 1:4, ncol = 2, label.size = 3) +
  theme_minimal()

summary(simple.linear.regression)

```

Data exploraion 

Variable Important 
```{r}
importance <- varImp(simple.linear.regression, scale=FALSE)

plot(importance, top=10)


```


```{r}
data.clean <- likehome.final %>%
  slice(c(20237,25924,29914))

likehome.final %>% filter(City=="New York City") %>%
  ggplot(aes(x=Property_type,y=Price,fill=Property_type)) + 
  geom_boxplot(alpha=0.3) +
  geom_point(data=data.clean, aes(x=Property_type,y=Price), color='red',size=3)+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))+
  xlab("")
  

likehome.final %>% filter(City=="New York City") %>%
  ggplot(aes(x=Room_type,y=Price,fill=Room_type)) + 
  geom_boxplot(alpha=0.3) +
  geom_point(data=data.clean, aes(x=Room_type,y=Price), color='red',size=3)+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))+
  xlab("")

likehome.final %>% filter(City=="New York City") %>%
  filter(Neighbourhood %in% c("Bayside","Brownsville","Mott Haven")) %>%
  ggplot(aes(x=Neighbourhood,y=Price,fill=Neighbourhood)) + 
  geom_boxplot(alpha=0.3) +
  geom_point(data=data.clean, aes(x=Neighbourhood,y=Price), color='red',size=3)+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))+
  xlab("")

likehome.final %>% filter(City=="New York City") %>%
  ggplot()+
  geom_jitter(aes(Review_scores_rating,Price))+
  geom_point(data=data.clean, aes(x=Review_scores_rating,y=Price), color='red',size=3)+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))+
  xlab("")



```
All of other predictors seem to be in a reasonable range, except for Review_Scores_rating showing that it is not original data but imputation. The median in rating might not truly reflect the value of these properties.

3.2. Stepwise Regression

```{r}

et.seed(2)

stepwise.linear.regression <- train(log(Price) ~. -ID -Zipcode -Review.missing -Bathrooms.missing -Bedrooms.missing -Zipcode.missing -Room_type.missing -City.missing,
                                    data = likehome.final,
                                    method = "glmStepAIC",
                                    direction= "backward",
                                    metric = "Rsquared",
                                    steps=0,
                                    trControl = train.control,
                                    trace = 0)


summary(stepwise.linear.regression)set.seed(2)

stepwise.linear.regression <- train(log(Price) ~. -ID -Zipcode -Review.missing -Bathrooms.missing -Bedrooms.missing -Zipcode.missing -Room_type.missing -City.missing,
                                    data = likehome.final,
                                    method = "glmStepAIC",
                                    direction= "backward",
                                    metric = "Rsquared",
                                    steps=0,
                                    trControl = train.control,
                                    trace = 0)


summary(stepwise.linear.regression)
formula(stepwise.linear.regression)
```


3.3. Lasso and Ridge Regression

```{r}

##Lasso Regression

set.seed(2)

tuning.grid <- expand.grid(lambda = 10^seq(2, -2, length = 100),
                           alpha = 1)

lasso.linear.regression <- train(log(Price) ~ .-ID -Zipcode -Review.missing -Bathrooms.missing -Bedrooms.missing -Zipcode.missing -Room_type.missing -City.missing,
                                 data = likehome.final,
                                 method = "glmnet",
                                 metric = "Rsquared",
                                 trControl = train.control,
                                 tuneGrid = tuning.grid)

coef(lasso.linear.regression$finalModel, lasso.linear.regression$bestTune$lambda)


#Ridge Regression

set.seed(2)

tuning.grid <- expand.grid(lambda = 10^seq(2, -2, length = 100),
                           alpha = 0)

ridge.linear.regression <- train(log(Price) ~ .-ID -Zipcode -Review.missing -Bathrooms.missing -Bedrooms.missing -Zipcode.missing -Room_type.missing -City.missing,
                                 data = likehome.final,
                                 method = "glmnet",
                                 metric = "Rsquared",
                                 trControl = train.control,
                                 tuneGrid = tuning.grid)

coef(ridge.linear.regression$finalModel, ridge.linear.regression$bestTune$lambda)

#Var Importance 

importance.2 <- varImp(lasso.linear.regression, scale=FALSE)

plot(importance.2, top=10)

importance.3 <- varImp(ridge.linear.regression, scale=FALSE)

plot(importance.3, top=10)



```

#Model Comparison

```{r}
resamps <- resamples(list(lm = simple.linear.regression,
                         lasso = lasso.linear.regression,
                         stepwise = stepwise.linear.regression,
                          ridge = ridge.linear.regression))

summary(resamps)
bwplot(resamps, layout = c(3, 1)) 
```

4.Check whether prices are competitive

```{r}

#Plot Price and Predicted Price of all observations 

likehome.final <- likehome.final %>%
  mutate(Predicted = predict(simple.linear.regression)) %>%
  mutate(Predicted=exp(Predicted)) %>%
  mutate(Residual=Price-Predicted)

likehome.final %>%
  ggplot()+
  geom_point(aes(Predicted,Price))+
  geom_smooth(mapping = aes(x = Predicted, y = Price),
              method = "lm", se = F) +
  theme_minimal()

#Plot Price and Predicted Price of ID 316332, 103303,652435

likehome.final.check <- likehome.final %>%
  filter(ID %in% c(316332, 103303,652435)) %>%
  mutate(Assessment = if_else(Price > Predicted, "Overpriced","Underpriced"))


likehome.final.check %>%
  ggplot(aes(Predicted,Price))+
  geom_point()+
  geom_smooth(mapping = aes(x = Predicted, y = Price),
              method = "lm", se = F) +
   theme_minimal()

#Check Price of other competitors that offer property that has same feature to 652435, since this property has price that lower than predicted but cannot be explained through investigation with predictors

likehome.final.1 <- likehome.final %>% filter(City=="Seattle" & Neighbourhood=="Minor" & Property_type=="Apartment" & Room_type=="Entire home/apt")

likehome.final.1 %>%
  ggplot()+
  geom_point(aes(Predicted,Price,color=Company))+
  geom_smooth(mapping = aes(x = Predicted, y = Price),
              method = "lm", se = F) +
   theme_minimal()


```

Further Analysis 

There is some price cluster that do not follow the linear regression: it seems that there is some underlying interactions between variables that their joint presence can strongly influence the price regardless of other elements

```{r}
likehome.final.analysis <- likehome.final %>%
  filter(Price %in% c(7200,8100,10800))
```

After analysis these price cluster, all the properties have the same common characteristics in Real Bed and Entire Home 

