---
title: "Individual Assignment"
output: html_document
---
```{r}
#tinytex::install_tinytex()
```

```{r}
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(ggpubr)

```


1. Data cleaning:

1.1. Check missing values and colume that contains most of missing value: 9728 obs out of 39344 obs contains NA, which means that nearly 25% obs would be obmitted due to NA. In order to retain sufficient obs to ensure the insights extracting from dataset, data imputatation will be conducted on variables that have lots of NA observation: Review_scores_rating, Room_type and Zipcode
```{r}
#Load data and package
getwd
setwd("C:/Users/Ha Nguyen/Desktop/Study Courses/Quarter 4/The Analytics Edge/Individual Assignment")

likehome <- read.csv2("LikeHome_GroupA (1).csv")

glimpse(likehome)
view(likehome)

#Mutate variables to factor
likehome <- likehome %>%
  mutate(Wifi =as.factor(Wifi),
         Aircon =as.factor(Aircon),
         Heating =as.factor(Heating),
         Free_parking =as.factor(Free_parking),
         Workspace =as.factor(Workspace),
         Tv =as.factor(Tv),
         Kitchen =as.factor(Kitchen),
         Washer =as.factor(Washer),
         Garden =as.factor(Garden),
         Waterfront =as.factor(Waterfront),
         Elevator =as.factor(Elevator),
         Fireplace =as.factor(Fireplace),
         Doorman =as.factor(Doorman),
         Balcony =as.factor(Balcony),
         Hot_tub =as.factor(Hot_tub),
         Pets =as.factor(Pets))

#Check vars with missing values
contains.missing <- likehome %>%
  filter_all(any_vars(is.na(.))) %>%
  select_if(function(x) any(is.na(x)))

contains.missing
view(contains.missing)



```

1.2. Data imputatation:

##Review_scores_rating: Imputate Review_score_rating by adding median value
```{r}
likehome <- likehome %>%
   mutate(Review.missing = as.factor(ifelse(is.na(Review_scores_rating), 1, 0)),
         Review_scores_rating = ifelse(is.na(Review_scores_rating),
                                      median(Review_scores_rating, na.rm = T),
                                      Review_scores_rating)) 
```

##Bathroom and Bedroom: Imputation by adding median value
```{r}
likehome <- likehome %>%
   mutate(Bathrooms.missing = as.factor(ifelse(is.na(Bathrooms), 1, 0)),
         Bathrooms = ifelse(is.na(Bathrooms), median(Bathrooms, na.rm = T), Bathrooms),
         Bedrooms.missing =  as.factor(ifelse(is.na(Bedrooms), 1, 0)),
         Bedrooms = ifelse(is.na(Bedrooms),median(Bedrooms, na.rm = T),Bedrooms))

```

#Zipcode, Room_type and City: Imputate NA as "Unknown"
```{r}
likehome <- likehome %>%
  mutate(Zipcode.missing = as.factor(ifelse(is.na(Zipcode), 1, 0)),
        Zipcode= ifelse(is.na(Zipcode),"Unknown",as.character(Zipcode)))

likehome <- likehome %>%
  mutate(Room_type.missing = as.factor(ifelse(is.na(Room_type), 1, 0)),
        Room_type= ifelse(is.na(Room_type),"Unknown",as.character(Room_type))) %>%
  mutate(Room_type=as.factor(Room_type))

likehome <- likehome %>%
  mutate(City.missing = as.factor(ifelse(is.na(City), 1, 0)),
        City= ifelse(is.na(City),"Unknown",as.character(City)))

```

#Fixing 5 Cities value: Boston and Los Angeles are messed up with mutiple entries referring the same city. As each city will have a unique identity in Zipcode range, we will use Zipcode as proxy to assign value back to these five cities

```{r}

likehome <- likehome %>%
  mutate(Zipcode = substr(Zipcode,1,5))

likehome <- likehome %>%
  mutate(Zipcode=as.integer(Zipcode)) 

likehome <- likehome %>%
  mutate(City = ifelse(Zipcode %in% (90000:93551),"Los Angeles",
                       ifelse(Zipcode %in% (10000:11695),"New York City",
                              ifelse(Zipcode %in% (94014:95202),"San Francisco",
                                     ifelse(Zipcode %in% (98101:98177),"Seattle",
                                            if_else(Zipcode %in% (2000:2467),"Boston",as.character(City)))))))

likehome <- likehome %>%
  mutate(Zipcode= if_else(is.na(Zipcode),"Unknown",as.character(Zipcode)))

unique(likehome$City)
```

The remaining City value except 5 cities are values that can not be assigned based on Zipcode because these ciies have "Unknown" Zipcode value. we will omit these cities and leave only 5 cities in the final data.


1.2. Invalid variables and observations: variables that contains only one-side argument will not have any impact on the analysis for difference among obs, therefore will be excluded. 

Futhermore, there are some obs that have numbers of beds is 0 but still have Bed_type, this will be considered as invalid data and thus also be excluded.

```{r}
##Vars that contains only one side argument 

contains.zero <- likehome %>%
  select_if(function(x) all(x==0) | all(x==1))

##filter only one-side argument
likehome <- likehome %>%
  select(!Balcony)

##Filter out rooms with no.of beds equals zero

unique(likehome$Bed_type)

likehome <- likehome %>%
  filter(!Beds==0)
```


1.3. Final data and final missing data

The final data include observations for five cities: Boston, Los Angeles, New York City, Seattle and San Francisco and will be filter out with all missing value.
So after the data imputation, we have included back lots of data points, reducing the omiited obs from 9728 to only 154 

```{r}
#Check vars with missing values after imputation
contains.missing.final <- likehome %>%
  filter_all(any_vars(is.na(.))) %>%
  select_if(function(x) any(is.na(x)))

#Final data for analysis: include Region 
likehome.final <- likehome %>%
  filter_all(all_vars(!is.na(.)))

likehome.final <- likehome.final %>%
  filter(City %in% c("Boston", "Los Angeles", "New York City", "Seattle","San Francisco")) %>%
mutate(City =  as.factor(City),
       Region=as.factor(if_else(City %in% c("New York City", "Boston"),"East Coast","West Coast")))


glimpse(likehome.final)

likehome.final %>% summary()

write.csv(likehome.final,"C:\\Users\\Ha Nguyen\\Desktop\\MyData.Likehome.csv", row.names = FALSE)

```


2. Descriptive analysis

2.1. Check correlations

```{r}
library(corrplot)
corrplot(cor(likehome.final[sapply(likehome.final, is.numeric)]),number.cex=0.7)
```


2.1. Exploratary Variables

#Distribution of continous numeric variables: 
```{r}

x <- likehome.final$Price
h1<-hist(x, breaks=10, col="red", xlab="Price Distribution",
   main="Histogram with Normal Curve")
xfit<-seq(min(x),max(x),length=40)
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x))
yfit <- yfit*diff(h1$mids[1:2])*length(x)
lines(xfit, yfit, col="blue", lwd=2)

likehome.final.1 <- likehome.final%>%
  mutate(Price =log(Price)) 

x <- likehome.final.1$Price
h2<-hist(x, breaks=10, col="red", xlab="Price Distribution",
   main="Histogram with Normal Curve after Log Transformation")
xfit<-seq(min(x),max(x),length=40)
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x))
yfit <- yfit*diff(h2$mids[1:2])*length(x)
lines(xfit, yfit, col="blue", lwd=2)

```
Price distribution is right-skewed. This means that we need to take the log value of Price to run the linear regression 

2.2. Rental objects in five cities

```{r}
##Rearrange factors: City following Eeast -> West, Property following ascending order in quantity
likehome.final$City <- factor(likehome.final$City,levels=c("Boston","New York City","Los Angeles","San Francisco","Seattle"))
likehome.final$Property_type <- factor(likehome.final$Property_type,levels=
c("Apartment","House","Condominium","Townhouse","Loft","Guesthouse","Bungalow","Villa","Serviced apartment"))


##How are the prices different among cities?
likehome.final %>%
  filter(Property_type %in% c( "Apartment", "House", "Condominium", "Loft", "Townhouse" )) %>%
  ggplot()+
  geom_boxplot(aes(reorder(City,Price,FUN=median),Price,fill=Property_type))+
  theme_minimal()+
  theme(axis.text.x = element_text(face="bold",size=9))+
  xlab("")+
  ylab("")+
  theme(legend.position="bottom")+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))

## Room_type - Bed_type and Price

likehome.final %>%
  ggplot()+
  geom_boxplot(aes(reorder(Bed_type,Price,FUN=median),Price,fill=Bed_type))+
  theme_minimal()+
  theme(axis.text.x = element_text(face="bold",size=9))+
  xlab("")+
  ylab("")+
  theme(legend.position="none")
  
likehome.final %>%
  filter(!Room_type=="Unknown") %>%
  ggplot()+
  geom_boxplot(aes(reorder(Room_type,Price,FUN=median),Price,fill=Room_type))+
  theme_minimal()+
  theme(axis.text.x = element_text(face="bold",size=9))+
  xlab("")+
  ylab("")+
  theme(legend.position="none")

##Dominant house types in each city - 5 most-rented property type

likehome.final %>%
  ggplot()+
  geom_bar(aes(City,fill=Property_type),position="stack",color="black")+
  theme_minimal()+
  xlab("")+
  ylab("")+
  theme(axis.text.x = element_text(face="bold",size=9))+
  theme(legend.position="bottom")

##Dominant house types in each city - excluding Apartment and House
likehome.final %>%
  filter(!Property_type %in% c( "Apartment", "House" )) %>%
  ggplot(aes(x=City, fill = Property_type))+
  geom_bar(position = "stack", stat = "count",color='black',width=0.9) +
  theme_minimal()+
  xlab("")+
  ylab("")+
  theme(axis.text.x = element_text(face="bold",size=9))+
  theme(legend.position="bottom")

##Room_type breadown by cities

percentData.room <- likehome.final %>% group_by(City) %>% count(Room_type) %>% 
  mutate(ratio=round(n*100/sum(n),0))

ggplot(percentData.room,aes(x=factor(City),y=ratio,fill=Room_type))+
    geom_bar(position="fill",color="black",stat = "identity")+
    geom_text(data=percentData.room, aes(y=n,label=paste0(ratio,"%")),position=position_fill(vjust=0.5))+
  scale_y_continuous(labels = scales::percent)+
  ylab("")+
  xlab("")+
  theme(axis.text.x = element_text(face="bold",size=9))+
  theme(legend.position="bottom")

```

```{r}
##Distributions of facilities across 5 cities
ggplot(terizon.train, aes(x=Perc_Equipment, fill=Churn)) + geom_density(position = 'fill') 



+
  facet_wrap(~City)
ggplot(likehome.final, aes(x=Price, fill=Wifi)) + geom_density(position = 'fill') +
  facet_wrap(~City)
ggplot(likehome.final, aes(x=Price, fill=Aircon)) + geom_density(position = 'fill') +
  facet_wrap(~City)
ggplot(likehome.final, aes(x=Price, fill=Heating)) + geom_density(position = 'fill') +
  facet_wrap(~City)
ggplot(likehome.final, aes(x=Price, fill=Free_parking)) + geom_density(position = 'fill') +
  facet_wrap(~City)
ggplot(likehome.final, aes(x=Price, fill=Workspace)) + geom_density(position = 'fill') +
  facet_wrap(~City)
ggplot(likehome.final, aes(x=Price, fill=Tv)) + geom_density(position = 'fill') +
  facet_wrap(~City)
ggplot(likehome.final, aes(x=Price, fill=Kitchen)) + geom_density(position = 'fill') +
  facet_wrap(~City)
ggplot(likehome.final, aes(x=Price, fill=Washer)) + geom_density(position = 'fill') +
  facet_wrap(~City)
ggplot(likehome.final, aes(x=Price, fill=Garden)) + geom_density(position = 'fill') +
  facet_wrap(~City)
ggplot(likehome.final, aes(x=Price, fill=Waterfront)) + geom_density(position = 'fill') +
  facet_wrap(~City)
ggplot(likehome.final, aes(x=Price, fill=Elevator)) + geom_density(position = 'fill') +
  facet_wrap(~City)
ggplot(likehome.final, aes(x=Price, fill=Fireplace)) + geom_density(position = 'fill') +
  facet_wrap(~City)
ggplot(likehome.final, aes(x=Price, fill=Doorman)) + geom_density(position = 'fill') +
  facet_wrap(~City)
ggplot(likehome.final, aes(x=Price, fill=Hot_tub)) + geom_density(position = 'fill') +
  facet_wrap(~City)

```

2.3 Competitive Landscape 
```{r}


#Market Porfolio: Monthly Revenue and Key Locations

#Quanity Sold: All market and across each property

#Bar

likehome.final %>%
  ggplot()+
  geom_bar(aes(x=Company,fill=Property_type),color="black",position = "stack",stat="count")+
  xlab("")+
  ylab("")+
  theme(axis.text.x = element_text(face="bold",size=11))+
  theme(legend.position="bottom")+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))

#Stacked bar
percentData.quant <- likehome.final %>% group_by(Property_type) %>% count(Company) %>% 
  mutate(ratio=round(n*100/sum(n),0))

ggplot(percentData.quant,aes(x=factor(Property_type),y=ratio,fill=Company))+
    geom_bar(position="fill",color="black",stat = "identity")+
    geom_text(data=percentData.quant, aes(y=ratio,label=paste0(ratio,"%")),position=position_fill(vjust=0.5))+
    scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07"))+
  scale_y_continuous(labels = scales::percent)+
  ylab("")+
  xlab("")+
  theme(legend.position="bottom")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))


##Monthly Revenue : Pie chart and Stacked bar

#Pie chart

percentData.rev <- likehome.final %>% 
  group_by(Company) %>% 
  summarise(Total = sum(Price, na.rm = TRUE)) %>%
  mutate(ratio=round(Total*100/sum(Total),0))


ggplot(percentData.rev, aes(x = "", y = ratio, fill = Company)) +
  geom_bar(width = 1, stat = "identity", color = "black") +
  coord_polar("y", start = 0)+
  geom_text(aes(y = ratio, label = paste0(ratio,"%")), color = "black", position = position_stack(vjust = 0.5))+
  scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07"))+
  ylab("")+
  xlab("")+
  theme_void()

#Stack Bar

percentData.rev.2 <- likehome.final %>% group_by(Property_type,Company) %>% 
  summarise(Total = sum(Price, na.rm = TRUE)) %>%
  mutate(ratio=round(Total*100/sum(Total),0))

ggplot(percentData.rev.2,aes(x=factor(Property_type),y=ratio,fill=Company))+
    geom_bar(position="fill",color="black",stat = "identity")+
    geom_text(data=percentData.rev.2, aes(y=ratio,label=paste0(ratio,"%")),position=position_fill(vjust=0.5))+
    scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07"))+
  scale_y_continuous(labels = scales::percent)+
  ylab("")+
  xlab("")+
  theme(legend.position="bottom")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))+
   theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))


#Price distributions of 3 companies
library(ggridges)
ggplot(likehome.final, aes(x = Price, y = Company)) +
  geom_density_ridges(aes(fill = Company)) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07"))+
  xlab("")+
  ylab("")+
  theme(legend.position="bottom")+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))


ggplot(likehome.final, aes(x = Property_type, y = Price, fill=Company)) +
  geom_boxplot() +
  scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07"))+
  xlab("")+
  ylab("")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))


#Room_type different among three companies
 theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))

percentData.room <- likehome.final %>% group_by(Company) %>% count(Room_type) %>% 
  mutate(ratio=round(n*100/sum(n),0))

ggplot(percentData.room,aes(x=factor(Company),y=ratio,fill=Room_type))+
    geom_bar(position="fill",color="black",stat = "identity")+
    geom_text(data=percentData.room, aes(y=ratio,label=paste0(ratio,"%")),position=position_fill(vjust=0.5))+
    scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07"))+
  scale_y_continuous(labels = scales::percent)+
  ylab("")+
  xlab("")+
  theme(legend.position="bottom")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))

#Price distributions of Room_type

likehome.final %>% filter(!Room_type=="Unknown") %>%
ggplot(aes(x = Room_type, y = Price, fill=Company)) +
  geom_boxplot() +
  scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07"))+
  xlab("")+
  ylab("")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))

```

```{r}
ggplot(likehome.final, aes(x=Price, fill=Pets)) + geom_density(position = 'fill') +
  facet_wrap(~Company)
ggplot(likehome.final, aes(x=Price, fill=Wifi)) + geom_density(position = 'fill') +
  facet_wrap(~Company)
ggplot(likehome.final, aes(x=Price, fill=Aircon)) + geom_density(position = 'fill') +
  facet_wrap(~Company)
ggplot(likehome.final, aes(x=Price, fill=Heating)) + geom_density(position = 'fill') +
  facet_wrap(~Company)
ggplot(likehome.final, aes(x=Price, fill=Free_parking)) + geom_density(position = 'fill') +
  facet_wrap(~Company)
ggplot(likehome.final, aes(x=Price, fill=Workspace)) + geom_density(position = 'fill') +
  facet_wrap(~Company)

```

Product Porfolio of 3 companies

```{r}

#2nd Address
percentData.company <- likehome.final %>% filter(!Property_type %in% c("Apartment", "House", "Condominium")) %>%
  group_by(Company, City) %>% count(Property_type) %>% 
  mutate(ratio=round(n*100/sum(n),0))


p1 <- percentData.company %>% filter(Company=="2nd Address") %>%
ggplot(aes(x=City,y=ratio,fill=Property_type))+
    geom_bar(position="fill",color="black",stat = "identity")+
  ylab("")+
  xlab("")+
  theme(legend.position="bottom")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))

p2 <- percentData.company %>% filter(Company=="LikeHome") %>%
ggplot(aes(x=City,y=ratio,fill=Property_type))+
    geom_bar(position="fill",color="black",stat = "identity")+
  ylab("")+
  xlab("")+
  theme(legend.position="bottom")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))

p3 <- percentData.company %>% filter(Company=="Common") %>%
ggplot(aes(x=City,y=ratio,fill=Property_type))+
    geom_bar(position="fill",color="black",stat = "identity")+
  ylab("")+
  xlab("")+
  theme(legend.position="bottom")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))

ggarrange(p1, p2, p3, ncol = 3, common.legend = TRUE) 
```




3. Price prediction

3.1. Simple linear regression
```{r}

#install.packages("future")
library(future)
plan(multiprocess, workers = 4)

require(caret)
require(ggfortify)

## Eliminate multicollinarity effect : Keeping Region and Country will lead to the multicollinariy effect

likehome.final <- likehome.final %>%
  select(!c(Region,Country))

train.control <- trainControl(method = "repeatedcv",
                              repeats = 10,
                              number = 10,
                              verboseIter = F)


#Simple linear regression

set.seed(2)

simple.linear.regression <- train(log(Price) ~. -ID -Zipcode -Review.missing -Bathrooms.missing -Bedrooms.missing -Zipcode.missing -Room_type.missing -City.missing,
                                  data = likehome.final,
                                  method = "lm",
                                  metric = "Rsquared",
                                  trControl = train.control)

autoplot(simple.linear.regression$finalModel, which = 1:4, ncol = 2, label.size = 3) +
  theme_minimal()

summary(simple.linear.regression)

```

Data exploraion 

Variable Important 
```{r}
importance <- varImp(simple.linear.regression, scale=FALSE)

plot(importance, top=10)


```


```{r}
data.clean <- likehome.final %>%
  slice(c(20237,25924,29914))

likehome.final %>% filter(City=="New York City") %>%
  ggplot(aes(x=Property_type,y=Price,fill=Property_type)) + 
  geom_boxplot(alpha=0.3) +
  geom_point(data=data.clean, aes(x=Property_type,y=Price), color='red',size=3)+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))+
  xlab("")
  

likehome.final %>% filter(City=="New York City") %>%
  ggplot(aes(x=Room_type,y=Price,fill=Room_type)) + 
  geom_boxplot(alpha=0.3) +
  geom_point(data=data.clean, aes(x=Room_type,y=Price), color='red',size=3)+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))+
  xlab("")

likehome.final %>% filter(City=="New York City") %>%
  filter(Neighbourhood %in% c("Bayside","Brownsville","Mott Haven")) %>%
  ggplot(aes(x=Neighbourhood,y=Price,fill=Neighbourhood)) + 
  geom_boxplot(alpha=0.3) +
  geom_point(data=data.clean, aes(x=Neighbourhood,y=Price), color='red',size=3)+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))+
  xlab("")

likehome.final %>% filter(City=="New York City") %>%
  ggplot()+
  geom_jitter(aes(Review_scores_rating,Price))+
  geom_point(data=data.clean, aes(x=Review_scores_rating,y=Price), color='red',size=3)+
  theme(legend.position="none")+
  theme(axis.text.x = element_text(face="bold",size=11,angle = 90))+
  theme(panel.background = element_blank())+
  theme(axis.line = element_line(colour = "black"))+
  xlab("")



```
All of other predictors seem to be in a reasonable range, except for Review_Scores_rating showing that it is not original data but imputation. The median in rating might not truly reflect the value of these properties.

3.2. Stepwise Regression

```{r}

et.seed(2)

stepwise.linear.regression <- train(log(Price) ~. -ID -Zipcode -Review.missing -Bathrooms.missing -Bedrooms.missing -Zipcode.missing -Room_type.missing -City.missing,
                                    data = likehome.final,
                                    method = "glmStepAIC",
                                    direction= "backward",
                                    metric = "Rsquared",
                                    steps=0,
                                    trControl = train.control,
                                    trace = 0)


summary(stepwise.linear.regression)set.seed(2)

stepwise.linear.regression <- train(log(Price) ~. -ID -Zipcode -Review.missing -Bathrooms.missing -Bedrooms.missing -Zipcode.missing -Room_type.missing -City.missing,
                                    data = likehome.final,
                                    method = "glmStepAIC",
                                    direction= "backward",
                                    metric = "Rsquared",
                                    steps=0,
                                    trControl = train.control,
                                    trace = 0)


summary(stepwise.linear.regression)
formula(stepwise.linear.regression)
```


3.3. Lasso and Ridge Regression

```{r}

##Lasso Regression

set.seed(2)

tuning.grid <- expand.grid(lambda = 10^seq(2, -2, length = 100),
                           alpha = 1)

lasso.linear.regression <- train(log(Price) ~ .-ID -Zipcode -Review.missing -Bathrooms.missing -Bedrooms.missing -Zipcode.missing -Room_type.missing -City.missing,
                                 data = likehome.final,
                                 method = "glmnet",
                                 metric = "Rsquared",
                                 trControl = train.control,
                                 tuneGrid = tuning.grid)

coef(lasso.linear.regression$finalModel, lasso.linear.regression$bestTune$lambda)


#Ridge Regression

set.seed(2)

tuning.grid <- expand.grid(lambda = 10^seq(2, -2, length = 100),
                           alpha = 0)

ridge.linear.regression <- train(log(Price) ~ .-ID -Zipcode -Review.missing -Bathrooms.missing -Bedrooms.missing -Zipcode.missing -Room_type.missing -City.missing,
                                 data = likehome.final,
                                 method = "glmnet",
                                 metric = "Rsquared",
                                 trControl = train.control,
                                 tuneGrid = tuning.grid)

coef(ridge.linear.regression$finalModel, ridge.linear.regression$bestTune$lambda)

#Var Importance 

importance.2 <- varImp(lasso.linear.regression, scale=FALSE)

plot(importance.2, top=10)

importance.3 <- varImp(ridge.linear.regression, scale=FALSE)

plot(importance.3, top=10)



```

#Model Comparison

```{r}
resamps <- resamples(list(lm = simple.linear.regression,
                         lasso = lasso.linear.regression,
                         stepwise = stepwise.linear.regression,
                          ridge = ridge.linear.regression))

summary(resamps)
bwplot(resamps, layout = c(3, 1)) 
```

4.Check whether prices are competitive

```{r}

#Plot Price and Predicted Price of all observations 

likehome.final <- likehome.final %>%
  mutate(Predicted = predict(simple.linear.regression)) %>%
  mutate(Predicted=exp(Predicted)) %>%
  mutate(Residual=Price-Predicted)

likehome.final %>%
  ggplot()+
  geom_point(aes(Predicted,Price))+
  geom_smooth(mapping = aes(x = Predicted, y = Price),
              method = "lm", se = F) +
  theme_minimal()

#Plot Price and Predicted Price of ID 316332, 103303,652435

likehome.final.check <- likehome.final %>%
  filter(ID %in% c(316332, 103303,652435)) %>%
  mutate(Assessment = if_else(Price > Predicted, "Overpriced","Underpriced"))


likehome.final.check %>%
  ggplot(aes(Predicted,Price))+
  geom_point()+
  geom_smooth(mapping = aes(x = Predicted, y = Price),
              method = "lm", se = F) +
   theme_minimal()

#Check Price of other competitors that offer property that has same feature to 652435, since this property has price that lower than predicted but cannot be explained through investigation with predictors

likehome.final.1 <- likehome.final %>% filter(City=="Seattle" & Neighbourhood=="Minor" & Property_type=="Apartment" & Room_type=="Entire home/apt")

likehome.final.1 %>%
  ggplot()+
  geom_point(aes(Predicted,Price,color=Company))+
  geom_smooth(mapping = aes(x = Predicted, y = Price),
              method = "lm", se = F) +
   theme_minimal()


```

Further Analysis 

There is some price cluster that do not follow the linear regression: it seems that there is some underlying interactions between variables that their joint presence can strongly influence the price regardless of other elements

```{r}
likehome.final.analysis <- likehome.final %>%
  filter(Price %in% c(7200,8100,10800))
```

After analysis these price cluster, all the properties have the same common characteristics in Real Bed and Entire Home 

